---
title: "Exploring Football Data with footwrap"
author: "Matthew Angoh, Shayla Tran, Zerui Zhang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Exploring Football Data with footwrap}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


##### Introduction
`footwrap` is an R package designed to serve as an API wrapper, allowing users to easily fetch and visualize football data from the RAPID-API. This vignette demonstrates how to use `footwrap` to access data on football teams, venues, coaches, player statistics, and compare trophies between players.

##### Getting Started
Ensure that you have installed and loaded `footwrap` into your session. This will also download its dependencies as well.


```{r setup}
# Load the footwrap package
library(footwrap)
```

##### Exploring the Functions
`footwrap` offers several functions to explore football data. Let's look at some of the key functions:

**1. Get Largest Venues by Country**

Use `GetBiggestVenues` to retrieve and visualize the largest venues in a given country.
```{r}
# Example: Get the 5 largest venues in England using mock data
GetBiggestVenues("England", 5, "<your_api_key>")
```

**2. Get Coach Information**

Fetch information about a team's coach with `GetCoachInfo`.
```{r}
# Example: Get coach information for a team using mock data
GetCoachInfo("team_id_example", "<your_api_key>")
```

**3. Compare Trophies Between Two Players**

Compare the number of trophies won by two players with `CompareTrophies`.
```{r}
# Example: Compare trophies between two players using mock data
CompareTrophies("player1_id", "player2_id", "<your_api_key>")
```

**4. Retrieve Team Statistics**

Access detailed team statistics for a specific league and season with `getTeamStatistics`.
```{r}
# Example: Retrieve statistics for Manchester United for the 2019 season
getTeamStatistics(39, 2019, "Manchester United", "<your_api_key>")
```

**5. Search Player Information**

Search for detailed information about a player by name and team with `searchPlayer`.
```{r}
# Example: Search for information about Ronaldo playing for Juventus
searchPlayer(name = "Ronaldo", team = "Juventus", apikey = "<your_api_key>")
```

**6. Retrieving Top Scorers**

`getTopScorers` provides an easy way to access the top scorers of any given league and season.
```{r}
# Example: Top Scorers in the Premier League for the 2020 Season
topScorers <- getTopScorers(39, 2020, "<your_api_key>")
```

**7. Fetching Top Assist Providers **

Similarly, `getTopAssists` focuses on the creative talents in the league, fetching data about players who provided the most assists.
```{r}
#Example: Premier League Top Assists in 2020
topAssists <- getTopAssists(39, 2020, "<your_api_key>")
```

**8. Accessing Football Fixtures**

With `getFootballFixtures`, users can retrieve detailed fixture lists for leagues, including match venues, dates, and scores, enabling fans and analysts to keep track of upcoming and past matches.

```{r}
# Example: Fetching Fixtures for the Premier League
fixtures <- getFootballFixtures(39, 2020, "<your_api_key>")
```

**9. Examining League Standings**

`getFootballStandings` offers a comprehensive view of the standings in any given league and season, providing insights into team performances, points, and rankings.
```{r}
# Example: Viewing Premier League Standings for 2020
standings <- getFootballStandings(39, 2020, "<your_api_key>")
```

**10. Analyzing Team Transfers **

Lastly, `getTeamTransfers` delves into the transfer market, offering data on player movements across teams, which is crucial for understanding team strategies and player careers.
```{r}
# Example: Checking Transfers for Manchester United
transfers <- getTeamTransfers(33, "<your_api_key>")
```

**11. Retrieve Player Statistics**

Utilize `getPlayerStatistics` to obtain an in-depth analysis of a player's performance across various metrics for a specified season, presented in a detailed gt table format.
```{r}
# Example: Retrieve statistics for a player (ID: 276) for the 2019 season
getPlayerStatistics(276, 2019, "<your_api_key>")
```

**12. Retrieve League Information by Name**

Use `getLeagueInfo` to effortlessly access details about any football league, including its ID and relevant attributes, by specifying its name, showcased in a concise dataframe format.

```{r}
# Example: Retrieve information about the Premier League
getLeagueInfo("Premier League", "<your_api_key>")
```



#####Conclusion

This vignette provides a brief overview of how to utilize the footwrap package to fetch and visualize football data. The package simplifies the process of accessing a wide range of football statistics and information, making it an invaluable tool for football enthusiasts and researchers alike. **Remember to keep your RAPID-API key secure and replace "your_api_key>" with your actual API key in the examples provided.**
