---
title: "Exploring Football Data with footwrap"
author: "Matthew Angoh, Shayla Tran, Zerui Zhang"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Exploring Football Data with footwrap}
  %\VignetteEngine{knitr::rmarkdown}
  \usepackage[utf8]{inputenc}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


##### Introduction
`footwrap` is an R package designed to serve as an API wrapper, allowing users to easily fetch and visualize football data from the RAPID-API. This vignette demonstrates how to use `footwrap` to access data on football teams, venues, coaches, player statistics, and compare trophies between players.

##### Getting Started
Before we dive into the functionalities of `footwrap`, ensure you have installed and loaded the package along with its dependencies.


```{r setup}
# Load the footwrap package
library(footwrap)

# Load the necessary libraries
library(httr)
library(tidyverse)
library(ggplot2)
library(jsonlite)
library(dplyr)
library(gt)
```

##### Exploring the Functions
`footwrap` offers several functions to explore football data. Let's look at some of the key functions:

**1. Get Largest Venues by Country**

Use `GetBiggestVenues` to retrieve and visualize the largest venues in a given country.
```{r}
# Example: Get the 5 largest venues in England using mock data
GetBiggestVenues("England", 5, "<your_api_key>")
```

**2. Get Coach Information**

Fetch information about a team's coach with `GetCoachInfo`.
```{r}
# Example: Get coach information for a team using mock data
GetCoachInfo("team_id_example", "<your_api_key>")
```

**3. Compare Trophies Between Two Players**

Compare the number of trophies won by two players with `CompareTrophies`.
```{r}
# Example: Compare trophies between two players using mock data
CompareTrophies("player1_id", "player2_id", "<your_api_key>")
```

**4. Retrieve Team Statistics**

Access detailed team statistics for a specific league and season with `getTeamStatistics`.
```{r}
# Example: Retrieve statistics for Manchester United for the 2019 season
getTeamStatistics(39, 2019, "Manchester United", "<your_api_key>")
```

**5. Search Player Information**

Search for detailed information about a player by name and team with `searchPlayer`.
```{r}
# Example: Search for information about Ronaldo playing for Juventus
searchPlayer(name = "Ronaldo", team = "Juventus", apikey = "your_api_key>")
```


#####Conclusion

This vignette provides a brief overview of how to utilize the footwrap package to fetch and visualize football data. The package simplifies the process of accessing a wide range of football statistics and information, making it an invaluable tool for football enthusiasts and researchers alike. Remember to keep your RAPID-API key secure and replace "your_api_key>" with your actual API key in the examples provided.
